Optical characterization of gaps in directly bonded Si compound optics using infrared spectroscopy

### 2015-09-25 AO_bondedSi.tex
some typos and re-arrange sections 4, 5.  not sure if I love it tho.

\section{Fabricating and embedded gaps of known axial and lateral extent}

@@

\section{Measurement technique and correlated measurement errors}
\label{sec_aboutErrors}

We measured transmission spectra through the bonded Si samples with an Agilent Cary 5000 UV-Vis-NIR spectrophotometer.  Table \ref{tabCary5000pars} lists the typical measurement settings and tool performance.

Measurement uncertainty can be characterized by both its \emph{bias} and \emph{variance} \cite{2013sdmm.book.....I}.  The bias is equivalent to a mean-level drift, which may be attributable to monochromator lamp luminosity drift.  The variance is the random sample-to-sample measurement residual remaining once the bias term is removed.  In our experiments, the bias term has an amplitude of 0.2\%, whereas the variance has an amplitude of 0.02\%.  Our measurement uncertainty is dominated by bias, not variance.

\section{Comparing the Fabry-P\'{e}rot model to data}

At this stage, \emph{any} regression technique can be employed to compare the Fabry-P model to data.  Least squares regression and other popular methods can be applied easily.  However, since least squares regression assumes zero bias, we elected to apply a Gaussian process regression technique that can handle biased measurements \cite{2013sdmm.book.....I,DFMgp,rasmussen2006gaussian}.  Given the relatively small bias amplitude (0.2\%), least squares regression and Gaussian process regression might yield similar solutions for the gap size, but least squares regression would drastically underestimate the \emph{uncertainty} value associated with the derived value of gap size\cite{DFMgp}.

\input{tbls/tbl_cary5000Pars.tex}

>>>>

\section{Embedded gaps of known axial and lateral extent}

@@

\section{Data}

We measured transmission spectra through the bonded Si samples with an Agilent Cary 5000 UV-Vis-NIR spectrophotometer.  Table \ref{tabCary5000pars} lists the typical measurement settings and tool performance.
\input{tbls/tbl_cary5000Pars.tex}

\subsection{Comparing the Fabry-P\'{e}rot model to data}

At this stage, \emph{any} regression technique can be employed to compare the Fabry-P\'{e}rot to data.  Least squares regression and other popular methods can be applied easily.

Our measurement uncertainty is dominated by \emph{bias}, not \emph{variance} \cite{2013sdmm.book.....I}.  The bias is similar to a mean-level drift, which may be attributable to monochromator lamp luminosity drift.  The variance is the random sample-to-sample measurement residual remaining once the bias term is removed.  In our experiments, the bias term has an amplitude of 0.2\%, whereas the variance has an amplitude of 0.02\%.

Since least squares regression assumes zero bias, we instead elected to apply a Gaussian process regression technique that can handle biased data \cite{2013sdmm.book.....I,DFMgp,rasmussen2006gaussian}.  Given the relatively small bias amplitude (0.2\%), least squares regression and Gaussian process regression might yield similar solutions for the gap size, but least squares regression would drastically underestimate the \emph{uncertainty} value associated with the derived value of gap size\cite{DFMgp}.
